---
title: "LongPron: Tracking Longitudinal L2 Pronunciation Research Longitudinally"
date: "Last Update: `r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    theme: spacelab
    highlight: espresso
bibliography: Longitudinal.bibtex
nocite: |
  @*
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width = "100%")
```

```{r, load-libs, echo = F, message = F, warning = F}
library("tidyr")
library("dplyr")
library("here")
library("janitor")
library("ggplot2")
library("knitr")
library("kableExtra")
library("forcats")
```

```{css, echo = F}
caption {
  color: black
}
p {
  font-size: 16px;
}
```

# Overview

**Statement of Purpose**  
This webpage is periodically updated with new longitudinal L2 pronunciation research that does not have a pronunciation-specific intervention. On this page, you can see the types of longitudinal studies that have been conducted up to this point, focusing on longitudinal design choices, such as study length and data points, and their intersection with participant sample and measurement characteristics. This page accompanies and builds upon

Nagle, C. L. (2021). Assessing the state of the art in longitudinal L2 pronunciation research: Trends and future directions. *Journal of Second Language Pronunciation*, *7*(2), 154-182. http://doi.org/10.1075/jslp.20059.nag

**Notes**  
I have reconfigured the data set from the format published and analyzed in Nagle (2021). In the updated data set, I treat each sample as an individual entry, which means that research reports that include multiple samples have multiple entries. By treating each sample as an individual entry in the data set, we can see how many unique longitudinal samples have been collected, including samples that were included in the same research report. Some researchers have analyzed the same group of participants in several reports, but it is not always clear if the sample is the exact same across reports, so I treat those samples as unique.

Research reports may have multiple samples for any of the following reasons: (1) L1 background, (2) age range, (3) context of learning. The "Multiple Entry" variable allows the data to be subset to exclude multiple entries to avoid double counting studies for certain tabulations, such as study length, data points, and so on. 

**Researchers**  
If you have published a longitudinal L2 pronunciation study that you think should be included in this webpage, please email me the citation so that I can review it and incorporate it if appropriate. Please note the following inclusion criteria: a study dealing with any aspect of L2 pronunciation learning that (1) tracked the same groups of participants over two or more data points, (2) did not include pronunciation-related training or a pronunciation-specific intervention, and (3) was published after 2006 in a peer-reviewed journal.

**Authors**  
If you believe that there has been an error in the coding for your article, please contact me.

**Users**  
If there is a particular cross-tabulation you're interested in but don't see it here, please contact me.

**My Contact Information**  
Charlie Nagle  
The University of Texas at Austin  
Email: cnagle[at]austin.utexas.edu

# Current Data Set

```{r, load-data, message = F}
long.data <- read.csv(
  file = here("New Longitudinal Research Synthesis.csv")) %>% 
  clean_names() %>% 
  mutate(length_bin = fct_relevel(length_bin, "0 to 4", "4 to 8", "8 to 12", "12 to 24", "24+"),
         participant_age_bin = fct_relevel(participant_age_bin, "Child", "Adolescent", "Adult"))
```

```{r, print-table}
long.data %>% 
  rmarkdown::paged_table()
```
<br>

# Publication Trends

```{r, gg-yearlypubs-longpron, fig.cap = "**Figure 1**. Longitudinal L2 Pronunciation Publications by Year", fig.dim = c(5, 4), warning = F}
long.data %>%
  filter(multiple_entry == "No") %>%
  ggplot(aes(x = study_year)) +
  geom_bar(stat = "count", color = "black", fill = "#56B4E9", width = 0.8) +
  theme_bw() +
  labs(x = "Publication Year", y = "Count") +
  scale_x_continuous(breaks = c(2006:2023))
```

<br>

# Longitudinal Characteristics

```{r, gg-lengthdatapoints, fig.cap = "**Figure 2**. Study Length by Data Points", fig.dim = c(5, 4), warning = F}
long.data %>%
  filter(multiple_entry == "No") %>%
  ggplot(aes(x = length_months, y = data_points_number, color = l2)) +
  geom_point(position = position_dodge(width = 2), alpha = 0.5, size = 3) +
  theme_bw() +
  labs(x = "Study Length in Months", y = "Study Data Points") +
  theme(legend.position = "bottom") +
  scale_y_continuous(breaks = c(2:8)) +
  scale_x_continuous(breaks = c(0, 4, 8, 12, 16, 20, 24), limits=c(0, 30))
```

<br>

```{r}
long.data %>%
  filter(multiple_entry == "No") %>%
  tabyl(length_bin, data_points_number) %>%
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined") %>%
  kable(caption = "**Table 1**. Study Length by Study Data Points") %>%
  kable_styling(bootstrap_options = c("bordered", "hover"))
```

<br>

#  Longitudinal Characteristics by Sample Characteristics

## Age Group

```{r, gg-lengthsample, fig.cap="**Figure 3**. Number of Unique Samples: Study Length by Learner Age Group", fig.dim = c(5, 3), warning = F}
long.data %>%
  ggplot(aes(x = length_bin)) + 
  geom_bar(stat = "count", color = "black", fill = "#56B4E9", width = 0.8) +
  theme_bw() +
  labs(x = "Study Length", y = "Count") +
  facet_wrap(~ participant_age_bin) +
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, vjust = .5))
```

<br>

## Context of Learning for Adult Learners

```{r, gg-pointssample, fig.cap = "**Figure 4**. Number of Unique Samples: Study Length by Context of Learning for Adult Learners", fig.dim = c(5, 3), warning = F}
long.data %>%
  filter(participant_age_bin == "Adult") %>%
  pivot_longer(cols = context_fl:context_sl,
               names_to = "context") %>%
  filter(value == "Yes") %>%
  ggplot(aes(x = data_points_number)) + 
  geom_bar(stat = "count", color = "black", fill = "#56B4E9", width = 0.8) +
  theme_bw() +
  labs(x = "Study Data Points", y = "Count") +
  facet_grid(~ context) +
  theme(strip.background=element_blank()) +
  scale_x_continuous(limits = c(1,9), breaks = c(2:8))
```
<br>

#  Longitudinal Characteristics by Measurement Characteristics

## Construct

```{r, gg-lengthconstruct, fig.cap = "**Figure 5**. Number of Unique Samples: Study Length by Construct", fig.dim = c(5, 3), warning = F}
long.data %>%
  pivot_longer(cols = perception:production_global,
               names_to = "construct") %>%
  filter(value == "Yes") %>%
  ggplot(aes(length_bin)) + 
  geom_bar(stat = "count", color = "black", fill = "#56B4E9", width = 0.8) +
  theme_bw() +
  labs(x = "Study Length", y = "Count") +
  facet_wrap(~ construct) +
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, vjust = .5))
```

<br>

```{r, gg-pointsconstruct, fig.cap = "**Figure 6**. Number of Unique Samples: Study Data Points by Construct", fig.dim = c(5, 3), warning = F}
long.data %>%
  pivot_longer(cols = perception:production_global,
               names_to = "construct") %>%
  filter(value == "Yes") %>%
  ggplot(aes(data_points_number)) + 
  geom_bar(stat = "count", color = "black", fill = "#56B4E9", width = 0.8) +
  theme_bw() +
  labs(x = "Study Data Points", y = "Count") +
  facet_wrap(~ construct) +
  theme(strip.background = element_blank()) +
  scale_x_continuous(limits = c(1, 9), breaks = c(2:8))
```

<br>

## Production Task

```{r, gg-lengthtask, fig.cap = "**Figure 7**. Number of Unique Samples: Study Length by Task Type", fig.dim = c(5, 3), warning = F}
long.data %>%
  pivot_longer(cols = task_controlled:task_spontaneous,
               names_to = "task") %>%
  filter(value == "Yes") %>%
  ggplot(aes(length_bin)) + 
  geom_bar(stat = "count", color = "black", fill = "#56B4E9", width = 0.8) +
  theme_bw() +
  labs(x = "Study Length", y = "Count") +
  facet_wrap(~ task) +
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, vjust = .5))
```

<br>

```{r, gg-pointstask, fig.cap = "**Figure 8**. Number of Unique Samples: Study Data Points by Task Type", fig.dim = c(5, 3), warning = F}
long.data %>%
  pivot_longer(cols = task_controlled:task_spontaneous,
               names_to = "task") %>%
  filter(value == "Yes") %>%
  ggplot(aes(data_points_number)) + 
  geom_bar(stat = "count", color = "black", fill = "#56B4E9", width = 0.8) +
  theme_bw() +
  labs(x = "Study Data Points", y = "Count") +
  facet_wrap(~ task) +
  theme(strip.background = element_blank()) +
  scale_x_continuous(limits = c(1, 9), breaks = c(2:8))
```

<br>

## Production Coding

```{r, gg-lengthcoding, fig.cap = "**Figure 9**. Number of Unique Samples: Study Length by Coding Approach", fig.dim = c(5, 3), warning = F}
long.data %>%
  mutate(linguistic_or_acoustic = coding_linguistic_or_acoustic_properties,
         expert_rating = coding_expert_rating,
         human_intuition = coding_human_intuition) %>%
  pivot_longer(cols = linguistic_or_acoustic:human_intuition,
               names_to = "coding_approach") %>%
  mutate(coding_approach = fct_relevel(coding_approach, c("linguistic_or_acoustic",
                                                          "expert_rating",
                                                          "human_intuition"))) %>%
  filter(value == "Yes") %>%
  ggplot(aes(length_bin)) + 
  geom_bar(stat = "count", color = "black", fill = "#56B4E9", width = 0.8) +
  theme_bw() +
  labs(x = "Study Length", y = "Count") +
  facet_wrap(~ coding_approach) +
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, vjust = .5))
```

<br>

```{r, gg-pointscoding, fig.cap = "**Figure 10**. Number of Unique Samples: Study Data Points by Coding Approach", fig.dim = c(5, 3), warning = F}
long.data %>%
  mutate(linguistic_or_acoustic = coding_linguistic_or_acoustic_properties,
         expert_rating = coding_expert_rating,
         human_intuition = coding_human_intuition) %>%
  pivot_longer(cols = linguistic_or_acoustic:human_intuition,
               names_to = "coding_approach") %>%
  mutate(coding_approach = fct_relevel(coding_approach, c("linguistic_or_acoustic",
                                                          "expert_rating",
                                                          "human_intuition"))) %>%
  filter(value == "Yes") %>%
  ggplot(aes(data_points_number)) + 
  geom_bar(stat = "count", color = "black", fill = "#56B4E9", width = 0.8) +
  theme_bw() +
  labs(x = "Study Data Points", y = "Count") +
  facet_wrap(~ coding_approach) +
  theme(strip.background = element_blank()) +
  scale_x_continuous(limits = c(1, 9), breaks = c(2:8))
```

<br>

# References
